SunPy - Python for Solar Physics

### 2014-01-28 3-5-Database.tex
small language tweaks in database subsection

Easy access to large quantities of solar data frequently leads to datafiles accumulating
in local storage such as laptops and desktop computers. Keeping data organised and available
is typically a cumbersome task for the average user. The file database is a sub-package of 
SunPy which is meant to solve this problem by providing a unified database to store and manage information about 
local data files. The database package was developed as part of the Google 
Summer Of Code (GSOC) program 2013.

The database sub-package makes use of a database supported by
\href{http://www.sqlalchemy.org}{SQLAlchemy}. This library was chosen
since it supports many SQL dialects. 
If SQLite is chosen, the database is stored as a single file which is
created automatically.A server-based database, on the other hand, could be used 
by a collaboration who work together from different machines on the
same data: a central database server stores all data and the clients connect to
it to read or write data.

>>>>

Easy access to large quantities of solar data frequently leads to datafiles accumulating
in local storage such as laptops and desktop computers. Keeping data organised and available
is typically a cumbersome task for the average user. The file database is a sub-package of 
SunPy which is meant to solve this problem by providing a unified database to store and manage information about 
local data files. The database package was developed as part of the Google 
Summer Of Code (GSoC) program 2013.

The database sub-package makes use of a database supported by
\href{http://www.sqlalchemy.org}{SQLAlchemy}. This library was chosen
since it supports many SQL dialects. 
If SQLite is selected, the database is stored as a single file which is
created automatically. A server-based database, on the other hand, could be used
by a collaboration who work together from different machines on the
same data: a central database server stores all data and the clients connect to
it to read or write data.
